Association between trauma severity models and opportunities for improvement:

### 2022-10-17 manuscript.Rmd
updates to results

@@

The odds ratio for TRISS was `r t.or["or"]` (95% CI: `r t.or["5 %"]`-`r t.or["95 %"]`). When plotting the ROC, the AUC was `r t.auc` (95% CI: `r t.auc.ci[1]`-`r t.auc.ci[3]`).

Other analyses 
--------------

<!-- Report other analyses done—eg analyses of subgroups and interactions,
and sensitivity analyses -->

>>>>

computed CIs for OR using wald estimator. 
<!--

@@

The odds ratio for TRISS was `r t.stats[['or']]` (95% CI: `r t.stats[['or.ci']]`, p-value: `r t.stats[['or.p']]`). When plotting the ROC, the AUC was `r t.stats[['auc']]` (95% CI: `r t.stats[['auc.ci']][1]`-`r t.stats[['auc.ci']][3]`). The odds ratio for NORMIT was `r n.stats[['or']]` (95% CI: `r n.stats[['or.ci']]`, p-value: `r n.stats[['or.p']]`). When plotting the ROC, the AUC was `r n.stats[['auc']]` (95% CI: `r n.stats[['auc.ci']][1]`-`r n.stats[['auc.ci']][3]`).
